Sequential Composition for Relaxed Memory: Pomsets with Predicate Transformers

### 2021-02-11 paper/outro.tex
submission
Draft of Fork-Join

For sequential composition, parallel composition and the conditional, we
believe that the definition is \emph{natural}, even \emph{canonical}.
For stores and loads, instead, the definition in Figure~\ref{fig:full} is a
Frankenstein's monster of features.  This complexity is \emph{essential},
however, not an accident of our poor choices.  Relaxed memory models must
please many audiences: compiler writers want one thing, hardware designers
another, and programmers yet another still.  The result is inevitably full of
compromise.

Given that \emph{complexity} cannot be eliminated from relaxed memory models, the
best one can do is attempt to understand its causes.  We have broken the
problem into eight manageable pieces, discussed throughout
\textsection\ref{sec:co}--\ref{sec:complications}.

>>>>

For sequential composition, parallel composition and the conditional, we
believe that the definition is \emph{natural}, even \emph{canonical}.
For stores and loads, instead, the definition in \reffig{fig:full} is a
Frankenstein's monster of features.  This complexity is \emph{essential},
however, not just an accident of our poor choices.  Relaxed memory models must
please many audiences: compiler writers want one thing, hardware designers
another, and programmers yet another still.  The result is inevitably full of
compromise.

Given that \emph{complexity} cannot be eliminated from relaxed memory models,
the best one can do is attempt to understand its causes.  We have broken the
problem into eight manageable pieces, discussed throughout
\textsection\ref{sec:q}--\ref{sec:complications}.  \refdef{def:pomsets-arm}
summarizes all the features necessary for efficient implementation on
\armeight{}.
